Improving \textsl{Gaia} parallax precision \\ with a data-driven model of stars

### 2017-06-06 paper/paper.tex
comment and typo
added sentences about selection function

  \cmd\ space.

@@

  the \tgas--\tmass\ intersection, the model \emph{is} representive of

@@

>>>>

  \cmd\ space. Thus, this has a small effect on our results, and could be improved by modelling the noise distribution simultaneously with the \cmd.

@@

  the \tgas--\tmass\ intersection, the model \emph{is} representative of

@@

  A similar argument can be made for \textit{internal} selection effects, such as inhomogeneities of the depth and noise distributions, which we have neglected. 
